Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-07 Tex/CAV2019/replyVSTTEJUNE2020.tex
revised paper and reply letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We thank you for asking us to comply with your reviewers' reports. 
We are submitting a revised version of our manuscript entitled 
``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro. 
This revised version carefully addresses each comment provided 
by the reviewers, as suggested in your original decision letter. 
In particular, our reply letter describes all modifications we made 
to our manuscript and the respective responses to the comments 
raised by the reviewers.

@@

The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions, which helped us significantly improve the quality of our manuscript.

According to the reviewers' comments, our manuscript has been carefully revised and all detailed changes are highlighted in red color, along with the original text. The revision included the Abstract, Introduction, Background, Synthesizing Optimal Sizing, Results, and Conclusions sections.

Our responses  to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed along our manuscript.

We hope those modifications in our manuscript and also our responses are sufficient to make our work suitable for publication.

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. Indeed, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. The paper was reviewed and the PV sizing modelling was changed to a more higher level of explanation. Different parts of the above mentioned sections in blue indicate where we changed/reviewed the text.

\end{resposta}

@@

\begin{resposta} 
We thank the reviewer again. Indeed, we had to revise the Abstract, the Introduction, and the Synthesizing Optimal Sizing sections in order to address more correctly what is PV optimal sizing. We must realize as well, and we added a highlight about this in the Results section, that a optimal solution from a tool is not necessarily the same optimal of other tool, mainly when the data base of equipment items (with different costs) are not the same.

\end{resposta}

@@

\begin{resposta} 
We thank the reviewer again for this insightful comment and suggestion. Indeed, we had to revise every section of the paper in order to address the specific issues highlighted by the reviewer......
Alessandro: Pra mim, é o desenvolvimento de uma técnica (como já discutimos em janeiro), que usa model checking e, como é feita em duas etapas, ela lembra o modo como o CEGIS funciona. E como o resultado é uma solução ótima, o resultado é uma otimização. Creio que isto deva ir pra introdução também (e pro abstract).

\end{resposta}

@@

\begin{resposta} 
Alessandro: Provavelmente eu tenha que melhorar o texto, pois a escolha de uma solução factível ou não achar uma solução factível já é por model checking ( e isso corresponde a 1a parte da técnica), a 2a parte é uma busca linear mas com teste de SUCCESS ou FAIL para gerar contraexemplo (e, pra mim, é model checking de novo).Pra mim, estamos aplicando model checking duas vezes na técnica. \textbf{Que achas?}  \textbf{Lucas: Concordo. Nao poderia aplicar uma busca binaria como fizemos no nosso journal do IJES?} 
acrescentei busca binária e $\nu Z$ na conclusão.

\end{resposta}

@@

\begin{resposta} 
Alessandro: Essa questão é para se pensar. Pra mim, a não linearidade das equações do artigo anterior de validação de sistemas solares estava mais claro pois usamos equações exponenciais e logaritmas. Nesse, a não linearidade se deve ao fato de a curva do ótimo global não ser contínua, pois pegamos valores específicos de variáveis não determinísticas, valores inteiros...daí eu não sei responder o que o revisor questionou.

Lucas: Modelamos essas usando aritmética de ponto flutuante. É apenas uma aproximação dos números reais. No entanto, neste trabalho, não nos preocupamos em calcular o erro de arredondamento. Precisamos enfatizar isso no texto. Esse nosso paper descreve um pouco sobre esses erros: https://arxiv.org/pdf/2004.12699.pdf

\end{resposta}

@@

\begin{resposta} 
Thank you. We appreciate the compliment.
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. He/she is right and it was the same observation did by Reviewer \#1. In order to correct this issue, we had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. The paper was reviewed and the PV sizing modelling was passed to a more higher level of explanation. Different parts of the paper in blue indicate where we changed/reviewed the text.

\end{resposta}

@@

\begin{resposta}
Preciso pensar aqui

\end{resposta}

@@

\begin{resposta}
We appreciate this Reviewer's suggestion. Indeed only with a double background and experience, specifically in computer science and in electrical engineering, is that is possible to realize that the tool (formal synthesis) can solve, and with remarkable results, the PV system sizing issue. Therefore we included a specific text in the Introduction section:
"However, formal methods and its application to synthesize PV systems are not explored in literature, mainly because it is necessary background and experience, at the same time, in computer science and PV systems, what is not so common."
\end{resposta}

@@

\begin{resposta}
The reviewer is right, we missed the details about why those values are taken. Therefore we reviewed the text to: "The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime".
\end{resposta}

@@

\begin{resposta}
We have updated the entire paragraph to explain the meaning of these variables as follows: ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq. (9) for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.''
\end{resposta}

@@

\begin{resposta} 
Repete o revisor 1. As mudanças que farei matam essas questões
\end{resposta}

 I do have some doubts about suitable the encodings that
  the authors choose, in particular, how relevant full fledged
  floating point reasoning is, but have no way to check.
  For a conference paper I am quite willing to give the paper a
  pass on this doubt as exposing details in the encodings could
  make the paper even less accessible.
- The paper contains several awkwardly formulated sentences. Examples
  are listed below.

@@

\begin{resposta}
Thank you.
\end{resposta}

@@

\begin{resposta}
We have rewritten this sentence as ``In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid [2]''.
\end{resposta}

>>>>

We thank you for asking us to comply with your reviewers' reports. We are submitting a revised version of our manuscript entitled  ``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro.  This revised version carefully addresses each comment provided by the reviewers, as suggested in the original notification.  In particular, our reply letter describes all modifications we have made to our manuscript and the respective responses to the comments raised by the reviewers.

@@

The authors would like to thank the anonymous reviewers for their valuable and constructive comments and suggestions, which helped us significantly improve our manuscript quality.

According to the reviewers' comments, our manuscript was carefully revised, and all detailed changes are highlighted in blue color, along with the original text. The revision included the Abstract, Introduction, Background, Synthesizing Optimal Sizing, Results, and Conclusions sections.

Our responses to all comments (in blue color) are given in the sequel, with clear indications about how and where they were addressed in our manuscript.

We hope those modifications in our manuscript and our responses are sufficient to make our work suitable for publication in the \textbf{12th Working Conference on Verified Software: Theories, Tools, and Experiments}.

@@

\begin{resposta} 
We thank the reviewer for these insightful comments and suggestions. We had to revise the Background and the Synthesizing Optimal Sizing sections to address the right conference attendants' profile. Our manuscript was entirely revised, and the PV sizing modeling was changed to a higher level of explanation, with a flowchart. The proposed synthesis algorithm followed the same principle. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF file that can be accessed.
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer again. Indeed, we had to revise the Abstract, the Introduction, and the Synthesizing Optimal Sizing sections in order to address more correctly what is PV optimal sizing. We must realize as well, and we added a highlight about this in the Results section. An optimal solution from a tool is not necessarily the same optimal of another tool, mainly when the database of equipment items (with different costs) are not the same. 
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer again for this insightful comment. We had to revise some specific parts of the paper, where the CEGIS technique, or optimization appeared (Abstract, Introduction, and Background sections). Our proposal is a technique based on CEGIS when considering the use of synthesis and automated verification. We aim to synthesize the optimal solution of a PV system (i.e., the technique produces an optimization). We expect that the revised sections can clarify the issue. \textcolor{red}{Which changes did you implement? please specify them here}.
\end{resposta}

@@

\begin{resposta} 
\textcolor{red}{where do we address this comment? Please indicate the section.}
We use four nondeterministic variables to hold four matrices with complete datasheet information from an equipment item. We have four variables and four matrices: one to PV panels, one to batteries, one to the inverter, and one to the charge controller. Those nondeterministic variables are used during the search for the feasible solution and controlled by the statements \textbf{assume}. The candidate solution is proposed in the phase {\sc Synthesize} of the technique. For the {\sc Verify} phase, we performed a linear search for the lowest cost, and the result is based on FAIL or SUCCESS check from a cost that is linearly incremented in this model. The model checking is used during this {\sc Verify} phase. If the process produces FAIL, then an optimal solution is found. If SUCCESS is provided, there is no feasible solution from the equipment list provided by the technique. We added a future work at the end of the CONCLUSIONS section, related to the possibility of speeding up the {\sc Verify} phase through binary search or even using specific optimization targeted solvers (as $\nu Z$).
\end{resposta}

@@

\begin{resposta} 
We model these PV sizing constraints using floating-point arithmetic. It is just an approximation of the real numbers. However, in this work, we are not concerned with calculating the rounding error, which is negligible when considering the size of the physical quantities and the variables adopted. We added this information at the end of Section 2.2. Therefore, we thank the reviewer for the question and the possibility of clarifying this issue in our manuscript.
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for these comments.
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. You are correct; Reviewer \#1 also provided the same observation. We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4). In Section 3, the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
\end{resposta}

@@

\begin{resposta}
Indeed the optimal sizing means the lowest cost from a feasible (technical) solution. When we compare just the LCC, you are correct: HOMER Pro produces the lowest values in most case-studies. However, we prove that using a simulation tool (PVsyst) with the optimal produced from our technique and HOMER, our technical solution is better to meet the house's requirements. We added two sentences in order to clarify this issue.

Section 4.4 Results: ``The cost of every equipment item used in HOMER Pro is a US-based cost, without adaptation regardless of where the equipment is installed.''

Section 4.5 Comparison Between Formal Synthesis and HOMER Pro: ``Related to the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil. The optimal solution presented by HOMER Pro is notoriously cheaper than our technique. However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, our technique is more indicated.'' 
\end{resposta}

@@

\begin{resposta}
We appreciate the reviewer's suggestion. Indeed only with background and experience, specifically in computer science and in electrical engineering, we can realize that the tool (formal synthesis) can solve, and with remarkable results, the PV system sizing issue. Therefore, we included a specific text in the Introduction section to address this particular comment:
``However, formal methods and its application to synthesize PV systems are not explored in literature, mainly because it is necessary background and experience, at the same time, in computer science and PV systems, what is not so common.''
\end{resposta}

@@

\begin{resposta}
We agree with the reviewer. We missed the details about why those values are taken. Therefore, we revised the corresponding online text to: ``The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime''.
\end{resposta}

@@

\begin{resposta}
We have updated the entire paragraph in the complementary online file to explain the meaning of these variables. ``The short circuit reference information ($I_{sc,ref}$) from the manufacturer's solar panel must be corrected because field temperature ($T$) is higher than nominal or laboratory temperature ($25^{\circ}C$), and the PV system is temperature dependent, as described by Eq. (9) for the ambient short-circuit current from the PV panel. $G$ is the solar irradiance from the deployment site, and $G_{ref}$ is defined as $1000$ $W/m^{2}$ by the manufacturers.''
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for these insightful comments and suggestions. Those are the same observations did by Reviewer \#1 and \#2. We had to revise the Background, and the Synthesizing Optimal Sizing sections in order to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4). In Section 3, the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
\end{resposta}

 I do have some doubts about suitable the encodings that
  the authors choose, in particular, how relevant full fledged
  floating point reasoning is, but have no way to check.
  For a conference paper I am quite willing to give the paper a
  pass on this doubt as exposing details in the encodings could
  make the paper even less accessible.

\begin{resposta}
Concerning the floating-point reasoning: we model the PV sizing constraints using floating-point arithmetic. It is just an approximation of the real numbers. However, in this work, we are not concerned with calculating the rounding error, which is negligible when considering the size of the physical quantities and the variables adopted. We added this information at the end of Section 2.2. Therefore, we thank the reviewer for the question and the possibility to clarify this issue in the paper.
\end{resposta}

- The paper contains several awkwardly formulated sentences. Examples
  are listed below.

@@

\begin{resposta}
We thank the reviewer.
\end{resposta}

@@

\begin{resposta}
We have rewritten this sentence as ``In $2017$, Abate suggested the application of formal methods to verify and control the behavior of devices in a smart grid [2]''.
\end{resposta}
